A Convolutional Neural Network for Outsole Recognition\tnoteref{t1}

### 2019-06-03 paper/paper.Rnw
Address comments

%\svp{Motivate the use of CNNs directly - complex model, higher level of feature aggregation. Mention pre-trained networks to transition.}
Convolutional neural networks (CNNs) are widely recognized as superior for novel image classification. CNNs are a form of artificial neural network which make use of the image convolution operator used by many low-level feature extraction methods.%\footnote{The Google Trends interest graph for CNNs and computer vision shows a massive increase in convolutional neural networks between mid-2014 and 2018 \url{https://trends.google.com/trends/explore?date=2010-01-01\%202019-02-18&q=convolutional\%20neural\%20network,computer\%20vision}}.
As CNNs have evolved, their architecture has become more complex, but the fundamental reliance on the image convolution operator sets CNNs apart from other artificial neural networks \citep{guRecentAdvancesConvolutional2018}. CNNs have deep architectures that can be trained to identify complex patterns, but they are structurally similar to the human visual architecture and output binary or probabilistic predictions for given labels that are readily interpretable. As CNNs make use of labeled training data, the predictions generated are for features which are similar to those identified by humans, resulting in models with greater face validity. Once a CNN is trained, it is relatively fast and easy to apply the model to new images and obtain classifications.

\svp{VGG16/ImageNet specifically. Note that the structure of the model is distinct from the fitted weights.}

\svp{Transfer Learning - using CNNs with less data. Make the point that this is what makes our method different from some of the others we've already cited - training a new classifier allows us to work within already-existing semantic contexts that examiners use.}

@@

Many convolutional neural networks have been trained on a set of images known as ImageNet; these images are hierarchically labeled, so the same image of a dog may have labels of sky, grass, and trees, and the dog may be labeled as ``mammal'', ``dog'', ``retriever'', and ``golden retriever'' at increasing levels of label complexity \citep{dengImageNetLargeScaleHierarchical}. CNNs trained on ImageNet are optimized for general human-like vision, that is, the ability to recognize a large set of different features simultaneously. As a result, the base of networks trained on these sets are often used for transfer learning, because the initial layers are broadly generalizable to a wide variety of more specific image labeling tasks.
\autoref{fig:vgg16layers} shows a selection of filters from VGG16, where each filter detects the presence of specific shapes or colors. Filters in earlier convolutional blocks detect simple features, such as colors and blobs, while later filters detect more complex combinations of features. Thus, a single image is made up of some combination of the hundreds of features that are detected by the filters in a CNN.

Transfer learning in neural network contexts involves freezing the weights of the pre-trained model base taken from a network trained on a more general set of images, so that during the training process, only the weights of the newly-added classifier are updated \citep{oquabLearningTransferringMidlevel2014}. In many cases, the entire model base is used, and fitted with a new model head; the modularity of CNNs makes this process relatively simple, and allows researchers to leverage pre-trained networks when working with diffierent sets of image data. Transfer learning allows CNNs to be applied to smaller datasets of several thousand images, reduces the amount of computational time required to fit the model, and provides boosted performance compared to training a new model from scratch \citep{yosinskiHowTransferableAre2014}. It has been successfully applied in automatic classification of medical images \citep{shinDeepConvolutionalNeural2016} as well as in various applications of shoe forensics \citep{kongCrossDomainForensicShoeprint2017,kongCrossDomainImageMatching2019a,zhangAdaptingConvolutionalNeural2017}.

>>>>

%\svp{Motivate the use of CNNs directly - complex model, higher level of feature aggregation. Mention pre-trained networks to transition.}
Convolutional neural networks (CNNs) are widely recognized as superior for novel image classification. CNNs are a form of artificial neural network which make use of the image convolution operator used by many low-level feature extraction methods.%\footnote{The Google Trends interest graph for CNNs and computer vision shows a massive increase in convolutional neural networks between mid-2014 and 2018 \url{https://trends.google.com/trends/explore?date=2010-01-01\%202019-02-18&q=convolutional\%20neural\%20network,computer\%20vision}}.
%As CNNs have evolved, their architecture has become more complex, but the fundamental reliance on the image convolution operator sets CNNs apart from other artificial neural networks \citep{guRecentAdvancesConvolutional2018}.
CNNs have deep architectures that can be trained to identify complex patterns, but they are structurally similar to the human visual architecture and output binary or probabilistic predictions for given labels that are readily interpretable. As CNNs make use of labeled training data, the predictions generated are for features which are similar to those identified by humans, resulting in models with greater face validity. Once a CNN is trained, it is relatively fast and easy to apply the model to new images and obtain classifications.

%\svp{VGG16/ImageNet specifically. Note that the structure of the model is distinct from the fitted weights.}
%\svp{Transfer Learning - using CNNs with less data. Make the point that this is what makes our method different from some of the others we've already cited - training a new classifier allows us to work within already-existing semantic contexts that examiners use.}
%\mt{Now that I can see the whole dang methods section, I think I prefer the order of the methods section as it is now, rather than the order suggested by the above comments, unless you disagree}

@@

Many convolutional neural networks have been trained on a set of images known as ImageNet; these images are hierarchically labeled, so the same image of a dog may have labels of sky, grass, and trees, and the dog may be labeled as ``mammal'', ``dog'', ``retriever'', and ``golden retriever'' at increasing levels of label complexity \citep{dengImageNetLargeScaleHierarchical}. CNNs trained on ImageNet are optimized for general human-like vision, that is, the ability to recognize a large set of different features simultaneously. As a result, the base of networks trained on these sets are often used for transfer learning, because the initial layers are broadly generalizable to a wide variety of more specific image labeling tasks. \autoref{fig:vgg16layers} shows a selection of filters from VGG16, where each filter detects the presence of specific shapes and colors. Filters in earlier convolutional blocks detect simple features, such as colors and blobs, while later filters detect more complex combinations of features. Each of the five convolutional blocks has between 128 and 1,536 filters, and a single image is made up of some combination of the thousands of features that are detected by those filters.

\fix{Transition needed?: The structure of the model is distinct from the fitted weights.} Transfer learning in neural network contexts involves freezing the weights of the pre-trained model base taken from a network trained on a more general set of images, so that during the training process, only the weights of the newly-added classifier are updated \citep{oquabLearningTransferringMidlevel2014}. In many cases, the entire model base is used, and fitted with a new model head; the modularity of CNNs makes this process relatively simple, and allows researchers to leverage pre-trained networks when working with diffierent sets of image data. Transfer learning allows CNNs to be applied to smaller datasets of several thousand images, reduces the amount of computational time required to fit the model, and provides boosted performance compared to training a new model from scratch \citep{yosinskiHowTransferableAre2014}. It has been successfully applied in automatic classification of medical images \citep{shinDeepConvolutionalNeural2016} as well as in various applications of shoe forensics \citep{kongCrossDomainForensicShoeprint2017,kongCrossDomainImageMatching2019a,zhangAdaptingConvolutionalNeural2017}.
